Weakly Nonlinear MRI: Notes

### 2014-02-07 notes/mri_notes.tex
Nondimensionalized induction eq

>>>>

We perform the same nondimensionalization for the induction equation: \\

\[\frac{\partial \widetilde{\mathbf{B}}}{\partial \widetilde{t}} \,  = \widetilde{\nabla} \times \left(\widetilde{\mathbf{u}} \times \widetilde{\mathbf{B}}\right) + \eta\widetilde{\nabla}^2 \widetilde{\mathbf{B}} \]

Which expands to become:

\[\frac{\partial \widetilde{\mathbf{B}}}{\partial \widetilde{t}} \, = \, \left(\widetilde{\mathbf{B}} \cdot \widetilde{\nabla} \right) \widetilde{\mathbf{u}} \, - \, \left(\widetilde{\mathbf{u}} \cdot \widetilde{\nabla} \right) \widetilde{\mathbf{B}} \, + \, \eta \widetilde{\nabla}^2\widetilde{\mathbf{B}} \] \\

After using the vector identity:

\[\nabla \times \left(\mathbf{u} \times \mathbf{B}\right) \, = \, \mathbf{u}\left(\nabla \cdot \mathbf{B}\right) \, - \, \mathbf{B}\left(\nabla \cdot \mathbf{u}\right) \, + \, \left(\mathbf{B} \cdot \nabla\right)\mathbf{u} \, - \, \left(\mathbf{u} \cdot \nabla\right)\mathbf{B} \] \\

And applying the incompressibility and solenoidal magnetic field constraints. \\

Substituting for the dimensional variables, the induction equation becomes: \\

\[\left(\Omega_0 B_0\right) \partial_t\mathbf{B} \, = \, \left(\Omega_0 B_0\right)\left(\mathbf{B} \cdot \nabla\right)\mathbf{u} \, - \, \left(\Omega_0 B_0\right)\left(\mathbf{u} \cdot \nabla \right)\mathbf{B} \, + \, \frac{\eta B_0}{\delta^2 r_0^2}\mathbf{B} \]

Which, after dividing by a factor of $\left(\Omega_0 B_0\right)$ and substituting in $R_m$, becomes: \\

\[\partial_t\mathbf{B} \, = \, \left(\mathbf{B} \cdot \nabla \right)\mathbf{u} \, -\, \left(\mathbf{u} \cdot \nabla \right)\mathbf{B} \, + \, \frac{1}{R_m}\mathbf{B} \]
